---
title: "data_extraction_datasets"
author: "Patrice Pottier"
date: "03/08/2021"
output: html_document
---

# load packages 
```{r}
library(tidyverse)
library(readxl)
library(here)
```

# Abayarathna et al. 2019

```{r}
## Duration of incubation period
inc_period <- read_excel(path = here("datasets", "Abayarathna_et_al_2019.xlsx"), sheet = "Inc period SVL mass")
inc_period  %>%
    group_by(Location, `Inc treatment`) %>% 
    summarise(mean(`Inc period (days)`))

## Heat tolerance at 2 weeks of age
HT_two_weeks <- read_excel(path = here("datasets", "Abayarathna_et_al_2019.xlsx"), sheet = "thermal tolerance 2 weeks")
HT_two_weeks %>%
    group_by(Site, `Inc treatment`) %>% 
    summarise(mean(`CT max°C`), sd(`CT max°C`), n=n(),
              mean(`SVL mm`), mean(`Mass g`))


## Heat tolerance at 6 weeks of age
HT_six_weeks <- read_excel(path = here("datasets", "Abayarathna_et_al_2019.xlsx"), sheet = "thermal tolerance 6 weeks")
HT_six_weeks %>%
    group_by(Site, `Inc Treatment`) %>% 
    summarise(mean(`CT max°C`), sd(`CT max°C`), n=n(),
              mean(`SVL mm`), mean(`Mass g`))

## Heat tolrance at 6 months of age, after recapture from the wild
HT_six_months <- read_excel(path = here("datasets", "Abayarathna_et_al_2019.xlsx"), sheet = "thermal tolerance 6 months")
HT_six_months %>%
    group_by(Site, `Inc Treatment`) %>% 
    summarise(mean(`CT max °C`) , sd(`CT max °C`), n=n())

```


# Asheim et al. 2020 

```{r}
Asheim<- read_csv("datasets/Asheim_et_al_2020.csv")

Asheim %>% 
    filter(rwTol!="NA") %>% 
    group_by(treatment) %>% 
    summarise(mean(rwTol), sd(rwTol), n=n(),
              mean(length_end, na.rm=T), mean(mass_end, na.rm=T))

Asheim %>% 
    filter(exclude==0 & swTol!="NA") %>% 
    group_by(treatment) %>% 
    summarise(mean(swTol), sd(swTol), n=n(),
              mean(length_end), mean(mass_end))
```

# Bai et al. 2019 

```{r}
bai <- read_excel(path = here("datasets", "Bai_et_al_2019.xls"), sheet = "CTmax")
bai %>%
    group_by(Time_recovery, Treatment) %>% 
    summarise(mean(CTmax), sd(CTmax), n=n())

```


# Dayananda et al. 2017 

```{r}
dayananda <- read_excel(path = here("datasets", "Dayananda_et_al_2017.xlsx"), sheet = "CTmax and CTmin")
dayananda  %>%
    filter(Ctmax...4!="NA") %>% 
    group_by(Loc, INC) %>% 
    summarise(mean(Ctmax...4), sd(Ctmax...4), n=n())
```


# Gibson et al. 2015

Note that organisation of the file was modified from the one published in supplementary materials.

```{r}
gibson<- read_csv("datasets/Gibson_et_al_2015.csv")
gibson %>% 
    group_by(experiment, Acclimation_temp, Rearing_temp) %>% 
    summarise(mean(Temp), sd(Temp), n=n(), mean(Mass))

```


# Gunderson et al. 2020 

```{r}
gunderson<- read_csv("datasets/Gunderson_et_al_2020.csv")
gunderson %>% 
    group_by(sex, treat) %>% 
    summarise(mean(ctmax), sd(ctmax), n=n(), mean(svl), mean(mass))
```

# Healy et al. 2019 

The files "SD_BR_plasticity_CTmax_data.txt" and "SC_PE_plasticity_CTmax_data.txt" from Dryad were combined into one file. 

```{r}
healy<- read.table("datasets/Healy_et_al_2019.txt", header=T)
healy %>% 
    group_by(pop, accTemp, devTemp, accTime) %>% 
    summarise(mean(ctmax), sd(ctmax), n=n())
```


# Illing et al. 2020 

Note that the first rows of the data from Dryad were trimmed to only keep the headers. 

```{r}
illing<- read_csv("datasets/Illing_et_al_2020.csv")
illing %>% 
    filter(CTmax!="NA") %>% 
    group_by(Species, Age, Rate, Treatment) %>% 
    summarise(mean(CTmax), sd(CTmax), n=n(), mean(SL, na.rm=T), bw=mean(BW, na.rm=T)/1000)
```



# Llewelyn et al. 2018 

```{r}
llewelyn<- read_csv("datasets/Llewelyn_et_al_2018.csv")
# CTmax after one month
llewelyn %>% 
    filter(oneMonthCTmax!="NA") %>% 
    group_by(population, incTemp) %>% 
    summarise(mean(oneMonthCTmax), sd(oneMonthCTmax), n=n())

# CTmax of adults

llewelyn %>% 
    filter(adultCTmax!="NA") %>% 
    group_by(population, incTemp) %>% 
    summarise(mean(adultCTmax), sd(adultCTmax), n=n())
```

# Moyano et al. 2018 

```{r}
moyano <- read_excel(path = here("datasets", "Moyano_et_al_2018.xlsx"), sheet = "CTmax_herring+seabass_Fig2")
moyano$`Body length (mm)`<-as.numeric(moyano$`Body length (mm)`)
moyano$`CTMax (°C)`<-as.numeric(moyano$`CTMax (°C)`)

moyano %>%
    filter(`CTMax (°C)`!="NA") %>% 
    group_by(Species, `Larval Stage`, `Age (days post-hatch)`,  `Warming rate (°C h-1)`, `Acclimation temperature (°C)`) %>% 
    summarise(mean(`CTMax (°C)`), sd(`CTMax (°C)`), n=n(), mean(`Body length (mm)`))
```


# Oyamaguchi et al. 2018 

```{r}
oyamaguchi<-read.table("datasets/Oyamaguchi_et_al_2018.txt", header=T) 
oyamaguchi<-filter(oyamaguchi,CT =="max", critical_temperature!="NA")
oyamaguchi %>% 
  group_by(temperature_raised) %>%
  summarize(acclim_duration = mean(days_acclim),
            ctmax = mean(critical_temperature),
            sd = sd(critical_temperature),
            n = n(),
            avg_mass = mean(mass_g),
            avg_size = mean(length_mm))

```


# Salachan and Sorensen 2017 


```{r}

# Animals at 9 days of age

sorensen_9d_4_19<- read.csv("datasets/Salachan_Sorensen_2017_9d_4_19.csv", sep=";", header=T)
sorensen_9d_4_19 %>% 
    group_by(ad.temp, ad.treat, dev.treat, dev.temp) %>% 
    summarise(mean(ctmax), sd(ctmax), n=n())

sorensen_9d_4_23<- read.csv("datasets/Salachan_Sorensen_2017_9d_4_23.csv", sep=";", header=T)
sorensen_9d_4_23 %>% 
    group_by(ad.temp, ad.treat, dev.treat, dev.temp) %>% 
    summarise(mean(ctmax), sd(ctmax), n=n())

sorensen_9d_8_19<- read.csv("datasets/Salachan_Sorensen_2017_9d_8_19.csv", sep=";", header=T)
sorensen_9d_8_19 %>% 
    group_by(ad.temp, ad.treat, dev.treat, dev.temp) %>% 
    summarise(mean(ctmax), sd(ctmax), n=n())

sorensen_9d_8_23<- read.csv("datasets/Salachan_Sorensen_2017_9d_8_23.csv", sep=";", header=T)
sorensen_9d_8_23 %>% 
    group_by(ad.temp, ad.treat, dev.treat, dev.temp) %>% 
    summarise(mean(ctmax), sd(ctmax), n=n())

```


# Salinas et al. 2019 

```{r}
salinas <- read_excel(path = here("datasets", "Salinas_et_al_2019.xlsx"), sheet = "Data")
salinas %>% 
    filter(CTmax!="NA") %>% 
    group_by(Treatment) %>% 
    summarise(mean(CTmax), sd(CTmax), n=n(), mean(Length7))
```

# Alford 2010 - Chapter 5

```{r}
alford <- read_excel(path = here("datasets", "Alford_2010.xlsx"), sheet = "Sheet1")

# Heat movement threshold
alford %>%
    filter(`Heat Movement Threshold` !="NA") %>% 
    group_by(Clone, Treatment) %>% 
    summarise(mean(`Heat Movement Threshold`), sd(`Heat Movement Threshold`), n=n())

# Heat coma temperature
alford %>%
    filter(`Heat Coma` !="NA") %>% 
    group_by(Clone, Treatment) %>% 
    summarise(mean(`Heat Coma`), sd(`Heat Coma`), n=n())
```
# Simon et al. 2015 

```{r}
simon<- read.csv("datasets/Simon_et_al_2015.csv", sep=";")
simon %>% 
    filter(CTMax!="NA") %>% 
    group_by(Species, Clutch, Acclimation) %>% 
    summarise(mean(CTMax), sd(CTMax), n=n())
```

# Spinks et al. 2019 

```{r}
spinks<- read.csv("datasets/Spinks_et_al_2019.csv")
spinks %>% 
    filter(CTM!="NA") %>% 
    group_by(Sex, Treatment) %>% 
    summarise(mean(CTM), sd(CTM), n=n(), mean(W), mean(SL))

```
# Terblanche and Chown 2006 

```{r}
terblanche_chown<- read_excel(path = here("datasets", "Terblanche_and_Chown_2006.xlsx"), sheet = "Sheet1")
terblanche_chown %>% 
    filter(Ctmax!="NA"&Trtmnt=="P") %>% 
    group_by(Treatment) %>% 
    summarise(mean(Ctmax), sd(Ctmax), n=n())
```

# Xue and Ma 2020 

```{r}
xue_ma<- read_excel(path = here("datasets", "Xue_and_Ma_2020.xlsx"), sheet = "Sheet1")
xue_ma %>% 
    filter(ctmax!="NA"&treatment!="H") %>% 
    group_by(sex, `mating status`, day, treatment) %>% 
    summarise(mean(ctmax), sd(ctmax), n=n())
```



# Gray 2013

```{r}
gray<- read_excel(path = here("datasets", "Gray_2013.xlsx"), sheet = "Sheet1")
gray %>% 
    filter(CTmax!="NA") %>% 
    group_by(larvaT, adultT) %>% 
    summarise(mean(CTmax), sd(CTmax), n=n(), mean(drymass))
```






