---
title: "data_extraction_LT50"
author: "Patrice Pottier"
date: "04/08/2021"
output: html_document
---

 R file to calculate LT50 from survival data at different test temperatures
 
```{r}
library(MASS) # For dose.p function
library(tidyverse)
```


# Billman et al. 2008

I used n=30 for the survival at each temperatures because authors used 10 animals * 3 replicates per test temperatures. 
```{r}
# LT50 for the 15C acclimation temperature. 
billman_15C<-data.frame(temp= c(17,26,27,28,29), 
                        alive=c(30, 30*0.9, 30*0.11, 30*0.06, 0),
                        dead=c(0, 30*0.1, 30*0.89, 30*0.94, 30))

mod.billman_15C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=billman_15C)
dose.p(mod.billman_15C, p=0.5)


# LT50 for the 18C acclimation temperature. 
billman_18C<-data.frame(temp= c(18,26,27,28,29),
                        alive=c(30, 30*0.933, 30*0.7, 30*0.9, 30*0.245),
                        dead=c(0, 30*0.067, 30*0.3, 30*0.1, 30*0.755))

mod.billman_18C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=billman_18C)
dose.p(mod.billman_18C, p=0.5)

# LT50 for the 23C acclimation temperature. 
billman_23C<-data.frame(temp= c(23, 28, 29, 30, 31), 
                        alive=c(30*0.934, 30*0.967, 30*0.8, 30*0.767, 0),
                        dead=c(30*0.066, 30*0.033, 30*0.2, 30*0.233, 30))

mod.billman_23C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=billman_23C)
dose.p(mod.billman_23C, p=0.5)

# LT50 for the 28C acclimation temperature. 
billman_28C<-data.frame(temp= c(28, 30, 31, 32), 
                        alive=c(30, 30*0.611, 0, 0),
                        dead=c(0, 30*0.389, 30, 30))

mod.billman_28C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=billman_28C)
dose.p(mod.billman_28C, p=0.5)
```

# Ineno et al. 2005 

I created a dataset with the data extracted from metaDigitise. 
Note that all data presented in the figures were extracted. However, many data points were irrelevant to calculate appropriate LT50 values and were discarded by the authors (see table 1). Moreover, to be included in our study, we needed comparable values at 10 and 14C incubation temperatures, which reduced the number of relevant observations even further. 
Below are presented only the relevant observations to calculate LT50.
```{r}
ineno<- read_csv("datasets/Ineno_et_al_2005.csv")
ineno$surv<-replace(ineno$surv, ineno$surv<0, 0) # Make sure to have true zeros
ineno$surv<-replace(ineno$surv, ineno$surv>100, 100) # Make sure to have true 100s

ineno <- ineno %>% 
    group_by(fig, strain, set_time, inc, temp) %>% 
    summarise(alive=(surv/100)*41, dead=41-alive)

#################################################################################################
###################### Embryos of the thermally selected strain #################################
#################################################################################################

########## Embryos at the early segmentation stage #################

# Early segmentation, 10C acclimated, 360 min survival 
TS_early_360_10C <- filter(ineno, fig=="1a"&set_time==360&inc==10)
mod_early_360_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_early_360_10C)
dose.p(mod_early_360_10C, p=0.5)

# Early segmentation, 14C acclimated, 360 min survival 
TS_early_360_14C <- filter(ineno, fig=="2a"&set_time==360&inc==14)
mod_early_360_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_early_360_14C)
dose.p(mod_early_360_14C, p=0.5) 

###

  
# Early segmentation, 10C acclimated, 720 min survival 
TS_early_720_10C <- filter(ineno, fig=="1a"&set_time==720&inc==10)
mod_early_720_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_early_720_10C)
dose.p(mod_early_720_10C, p=0.5)

# Early segmentation, 14C acclimated, 720 min survival 
TS_early_720_14C <- filter(ineno, fig=="2a"&set_time==720&inc==14)
mod_early_720_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_early_720_14C)
dose.p(mod_early_720_14C, p=0.5) 

###

  
# Early segmentation, 10C acclimated, 1440 min survival 
TS_early_1440_10C <- filter(ineno, fig=="1a"&set_time==1440&inc==10)
mod_early_1440_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_early_1440_10C)
dose.p(mod_early_1440_10C, p=0.5)

# Early segmentation, 14C acclimated, 1400 min survival 
TS_early_1440_14C <- filter(ineno, fig=="2a"&set_time==1440&inc==14)
mod_early_1440_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_early_1440_14C)
dose.p(mod_early_1440_14C, p=0.5) 

######## Embryos at the neurula stage ##################


# neurula, 10C acclimated, 720 min survival 
TS_neur_720_10C <- filter(ineno, fig=="1e"&set_time==720&inc==10)
mod_neur_720_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_neur_720_10C)
dose.p(mod_neur_720_10C, p=0.5)

# neurula, 14C acclimated, 720 min survival 
TS_neur_720_14C <- filter(ineno, fig=="2e"&set_time==720&inc==14)
mod_neur_720_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_neur_720_14C)
dose.p(mod_neur_720_14C, p=0.5) 

###

  
# neurula, 10C acclimated, 1440 min survival 
TS_neur_1440_10C <- filter(ineno, fig=="1e"&set_time==1440&inc==10)
mod_neur_1440_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_neur_1440_10C)
dose.p(mod_neur_1440_10C, p=0.5)

# neurula, 14C acclimated, 1400 min survival 
TS_neur_1440_14C <- filter(ineno, fig=="2e"&set_time==1440&inc==14)
mod_neur_1440_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =TS_neur_1440_14C)
dose.p(mod_neur_1440_14C, p=0.5) 


########################################################################################################
############################# Embryos of the Donaldson strain ##########################################
########################################################################################################



########## Embryos at the early segmentation stage #################


# Early segmentation, 10C acclimated, 360 min survival 
donaldson_early_360_10C <- filter(ineno, fig=="1b"&set_time==360&inc==10)
mod_early_360_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_early_360_10C)
dose.p(mod_early_360_10C, p=0.5)

# Early segmentation, 14C acclimated, 360 min survival 
donaldson_early_360_14C <- filter(ineno, fig=="2b"&set_time==360&inc==14)
mod_early_360_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_early_360_14C)
dose.p(mod_early_360_14C, p=0.5) 

###

  
# Early segmentation, 10C acclimated, 720 min survival 
donaldson_early_720_10C <- filter(ineno, fig=="1b"&set_time==720&inc==10)
mod_early_720_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_early_720_10C)
dose.p(mod_early_720_10C, p=0.5)

# Early segmentation, 14C acclimated, 720 min survival 
donaldson_early_720_14C <- filter(ineno, fig=="2b"&set_time==720&inc==14)
mod_early_720_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_early_720_14C)
dose.p(mod_early_720_14C, p=0.5) 



################### Embryos at the neurula stage ##################

# neurula, 10C acclimated, 720 min survival 
donaldson_neur_720_10C <- filter(ineno, fig=="1f"&set_time==720&inc==10)
mod_neur_720_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_neur_720_10C)
dose.p(mod_neur_720_10C, p=0.5)

# neurula, 14C acclimated, 720 min survival 
donaldson_neur_720_14C <- filter(ineno, fig=="2f"&set_time==720&inc==14)
mod_neur_720_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_neur_720_14C)
dose.p(mod_neur_720_14C, p=0.5) 

###

  
# neurula, 10C acclimated, 1440 min survival 
donaldson_blast1440_10C <- filter(ineno, fig=="1f"&set_time==1440&inc==10)
mod_blast1440_10C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_blast1440_10C)
dose.p(mod_blast1440_10C, p=0.5)

# neurula, 14C acclimated, 1400 min survival 
donaldson_blast1440_14C <- filter(ineno, fig=="2f"&set_time==1440&inc==14)
mod_blast1440_14C<-glm(cbind(alive, dead)~ temp, family=binomial, data =donaldson_blast1440_14C)
dose.p(mod_blast1440_14C, p=0.5) 


```


# Sakurai et al. 2021
```{r}
# LT50 for the group acclimated to the lower temperature
sakurai_LA<-data.frame(temp= c(21.8, 24.2, 25.8, 27.8), 
                        alive=c(10, 10, 0, 0),
                        dead=c(0, 0, 10, 10))

mod.sakurai_LA<-glm(cbind(alive, dead) ~ temp, family=binomial, data=sakurai_LA)
dose.p(mod.billman_15C, p=0.5)


# LT50 for the group acclimated to the higher temperature

sakurai_HA<-data.frame(temp= c(21.8, 24.2, 25.8, 27.8, 30.3),
                        alive=c(10, 10, 10, 10, 0),
                        dead=c(0, 0, 0, 0, 10))

mod.sakurai_HA<-glm(cbind(alive, dead) ~ temp, family=binomial, data=sakurai_HA)
dose.p(mod.sakurai_HA, p=0.5)

```

# Tsuchida and Setoguma 1997 

We can convert survival at different temperatures to the temperature animals can tolerate for 1 hour according to Jorgensen et al. 2021 

See script at https://github.com/MOersted/Thermal-tolerances/blob/main/TDT_from_Static.R

```{r}
static = data.frame(group=c("15C_acc", "15C_acc", "15C_acc", "15C_acc", "20C_acc", "20C_acc", "20C_acc", "20C_acc", "25C_acc", "25C_acc", "25C_acc", "25C_acc", "28C_acc", "28C_acc", "28C_acc", "28C_acc", "28C_acc", "28C_acc"), 
                    t_coma=c(79, 125, 143, 225, 83, 130, 230, 520, 112, 236, 640, 1730, 53, 97, 193, 590, 1200, 2310), 
                    assay_temp=c(30, 29.5, 29, 28.4, 31, 30.5, 30, 29.6, 31.5, 31, 30.4, 30, 32.9, 32.4, 31.9, 31.5, 31, 30.5))


mod.15C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="15C_acc"))
chemCal::inverse.predict(mod.15C, log10(60))
chemCal::inverse.predict(mod.15C, 0)

mod.20C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="20C_acc"))
chemCal::inverse.predict(mod.20C, log10(60))
chemCal::inverse.predict(mod.20C, 0)

mod.25C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="25C_acc"))
chemCal::inverse.predict(mod.25C, log10(60))
chemCal::inverse.predict(mod.25C, 0)

mod.28C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="28C_acc"))
chemCal::inverse.predict(mod.28C, log10(60))
chemCal::inverse.predict(mod.28C, 0)
```

# Wagner et al. 2001 

Note that the data for the BV population was not possible to estimate because the mortality was higher at low vs. high temperatures. 
```{r}
# LT50 for the BL population acclimated to 13.6C
wagner_BL_low<-data.frame(temp= c(23, 23.5, 24), 
                        alive=c(10*0.8, 10*0.633, 0),
                        dead=c(10*0.2, 10*0.367, 10))

mod.wagner_BL_low<-glm(cbind(alive, dead) ~ temp, family=binomial, data=wagner_BL_low)
dose.p(mod.wagner_BL_low, p=0.5)


# LT50 for the BL population acclimated to 18C

wagner_BL_high<-data.frame(temp= c(23.2, 23.7, 23.9, 24.2, 24.5),
                        alive=c(10, 10*0.1, 10*0.85, 10*0.267, 0),
                        dead=c(0, 10*0.9, 10*0.15, 10*0.733, 10))

mod.wagner_BL_high<-glm(cbind(alive, dead) ~ temp, family=binomial, data=wagner_BL_high)
dose.p(mod.wagner_BL_high, p=0.5)


# LT50 for the SN population acclimated to 13.6C
wagner_SN_low<-data.frame(temp= c(23, 23.5, 24), 
                        alive=c(10*0.867, 10*0.967, 0),
                        dead=c(10*0.133, 10*0.033, 10))

mod.wagner_SN_low<-glm(cbind(alive, dead) ~ temp, family=binomial, data=wagner_SN_low)
dose.p(mod.wagner_SN_low, p=0.5)


# LT50 for the SN population acclimated to 18C

wagner_SN_high<-data.frame(temp= c(23.2, 23.7, 23.9, 24.2, 24.5),
                        alive=c(10, 10*0.05, 10*0.25, 10*0.133, 0),
                        dead=c(0, 10*0.95, 10*0.75, 10*0.867, 10))

mod.wagner_SN_high<-glm(cbind(alive, dead) ~ temp, family=binomial, data=wagner_SN_high)
dose.p(mod.wagner_SN_high, p=0.5)



# LT50 for the EL population acclimated to 13.6C
wagner_EL_low<-data.frame(temp= c(23, 23.5, 24), 
                        alive=c(10*0.8, 10*0.767, 10*0.267),
                        dead=c(10*0.2, 10*0.233, 10*0.733))

mod.wagner_EL_low<-glm(cbind(alive, dead) ~ temp, family=binomial, data=wagner_EL_low)
dose.p(mod.wagner_EL_low, p=0.5)


# LT50 for the EL population acclimated to 18C

wagner_EL_high<-data.frame(temp= c(23.2, 23.7, 23.9, 24.2, 24.5),
                        alive=c(10*0.967, 10*0.486, 10*0.9, 10*0.148, 10*0.25),
                        dead=c(10*0.033, 10*0.514, 10*0.1, 10*0.852, 10*0.75))

mod.wagner_EL_high<-glm(cbind(alive, dead) ~ temp, family=binomial, data=wagner_EL_high)
dose.p(mod.wagner_EL_high, p=0.5)
```

# Benedict et al. 1991 

```{r}
# LT50 for the animals acclimated to 25C 

benedict_25C<-data.frame(temp= c(30, 37, 38.5, 40, 41.5, 43),
                        alive=c(100, 100, 100*0.997, 100*0.92, 100*0.793, 0),
                        dead=c(0, 0, 100*0.003, 100*0.08, 100*0.707, 100))

mod.benedict_25C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=benedict_25C)
dose.p(mod.benedict_25C, p=0.5)



benedict_30C<-data.frame(temp= c(30, 37, 38.5, 40, 41.5, 43, 44.5),
                        alive=c(100, 100, 100, 100, 100*0.918, 100*0.013, 0),
                        dead=c(0, 0, 0, 0, 100*0.087, 100*0.987, 100))

mod.benedict_30C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=benedict_30C)
dose.p(mod.benedict_30C, p=0.5)
```

# Cai and Chen 2005 

```{r}
######### P. menodon ############

# Data for P. menodon acclimated to 25C 

cai_chen_menodon_25C<-data.frame(temp= c(34, 35, 36, 37, 38, 39, 40),
                        alive=c(20, 20, 20*0.95, 20*0.75, 20*0.15, 0, 0),
                        dead=c(0, 0, 20*0.05, 20*0.25, 20*0.85, 20, 20))

mod.cai_chen_menodon_25C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_menodon_25C)
dose.p(mod.cai_chen_menodon_25C, p=0.5)

# Data for P. menodon acclimated to 28C 

cai_chen_menodon_28C<-data.frame(temp= c(34, 35, 36, 37, 38, 39, 40),
                        alive=c(20, 20, 20*0.95, 20*0.9, 20*0.2, 0, 0),
                        dead=c(0, 0, 20*0.05, 20*0.1, 20*0.8, 20, 20))

mod.cai_chen_menodon_28C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_menodon_28C)
dose.p(mod.cai_chen_menodon_8C, p=0.5)

# Data for P. menodon acclimated to 31C 

cai_chen_menodon_31C<-data.frame(temp= c(35, 36, 37, 38, 39, 40),
                        alive=c(20, 20, 20*0.9, 20*0.4, 0, 0),
                        dead=c(0, 0, 20*0.01, 20*0.6, 20, 20))

mod.cai_chen_menodon_31C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_menodon_31C)
dose.p(mod.cai_chen_menodon_31C, p=0.5)

# Data for P. menodon acclimated to 34C 

cai_chen_menodon_34C<-data.frame(temp= c(35, 36, 37, 38, 38.5, 39, 40),
                        alive=c(20, 20, 20*0.95, 20*0.55, 20*0.2, 0, 0),
                        dead=c(0, 0, 20*0.05, 20*0.45, 20*0.8, 20, 20))

mod.cai_chen_menodon_34C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_menodon_34C)
dose.p(mod.cai_chen_menodon_34C, p=0.5)

# Data for P. menodon acclimated to 35C 

cai_chen_menodon_35C<-data.frame(temp= c(35, 36, 37, 38, 38.5, 39, 40),
                        alive=c(20, 20, 20*0.95, 20*0.6, 20*0.2, 0, 0),
                        dead=c(0, 0, 20*0.05, 20*0.4, 20*0.8, 20, 20))

mod.cai_chen_menodon_35C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_menodon_35C)
dose.p(mod.cai_chen_menodon_35C, p=0.5)


########## M. affinis ################

# Data for P. affinis acclimated to 25C 

cai_chen_affinis_25C<-data.frame(temp= c(36, 37, 38, 39, 40, 41, 42),
                        alive=c(20, 20, 20*0.95, 20*0.45, 0, 0, 0),
                        dead=c(0, 0, 20*0.05, 20*0.55, 20, 20, 20))

mod.cai_chen_affinis_25C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_affinis_25C)
dose.p(mod.cai_chen_affinis_25C, p=0.5)

# Data for P. affinis acclimated to 28C 

cai_chen_affinis_28C<-data.frame(temp= c(36, 37, 38, 39, 40, 41, 42),
                        alive=c(20, 20, 20, 20*0.55, 20*0.15, 0, 0),
                        dead=c(0, 0, 0, 20*0.45, 20*0.85, 20, 20))

mod.cai_chen_affinis_28C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_affinis_28C)
dose.p(mod.cai_chen_affinis_28C, p=0.5)

# Data for P. affinis acclimated to 31C 

cai_chen_affinis_31C<-data.frame(temp= c(36, 37, 38, 39, 40, 41, 42),
                        alive=c(20, 20, 20, 20*0.55, 20*0.2, 0, 0),
                        dead=c(0, 0, 0, 20*0.45, 20*0.8, 20, 20))

mod.cai_chen_affinis_31C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_affinis_31C)
dose.p(mod.cai_chen_affinis_31C, p=0.5)

# Data for P. affinis acclimated to 34C 

cai_chen_affinis_34C<-data.frame(temp= c(36, 37, 38, 39, 40, 41, 42),
                        alive=c(20, 20, 20, 20*0.6, 20*0.2, 0, 0),
                        dead=c(0, 0, 0, 20*0.4, 20*0.8, 20, 20))

mod.cai_chen_affinis_34C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_affinis_34C)
dose.p(mod.cai_chen_affinis_34C, p=0.5)

# Data for P. affinis acclimated to 37C 

cai_chen_affinis_37C<-data.frame(temp= c(36, 37, 38, 39, 40, 41, 42),
                        alive=c(20, 20, 20, 20*0.6, 20*0.3, 0, 0),
                        dead=c(0, 0, 0, 20*0.4, 20*0.7, 20, 20))

mod.cai_chen_affinis_37C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_affinis_37C)
dose.p(mod.cai_chen_affinis_37C, p=0.5)


# Data for P. affinis acclimated to 38C 

cai_chen_affinis_38C<-data.frame(temp= c(36, 37, 38, 39, 40, 41, 42),
                        alive=c(20, 20, 20, 20*0.65, 20*0.2, 0, 0),
                        dead=c(0, 0, 20, 20*0.35, 20*0.8, 20, 20))

mod.cai_chen_affinis_38C<-glm(cbind(alive, dead) ~ temp, family=binomial, data=cai_chen_affinis_38C)
dose.p(mod.cai_chen_affinis_38C, p=0.5)

```


# Chen and Chen 1999 

```{r}
#################### 25 ppt salinity #######################

# Data for animals acclimated to 20C, at 25 ppt salinity

chen_chen_20C_25ppt<-data.frame(temp= c(30, 31, 32, 33, 34),
                        alive=c(19, 14, 10, 2, 0),
                        dead=c(1, 6, 10, 18, 20))

mod.chen_chen_20C_25ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_20C_25ppt)
dose.p(mod.chen_chen_20C_25ppt, p=0.5)


# Data for animals acclimated to 25C, at 25 ppt salinity

chen_chen_25C_25ppt<-data.frame(temp= c(31, 32, 33, 34, 35),
                        alive=c(18, 12, 3, 0, 0),
                        dead=c(2, 8, 17, 20, 20))

mod.chen_chen_25C_25ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_25C_25ppt)
dose.p(mod.chen_chen_25C_25ppt, p=0.5)


# Data for animals acclimated to 30C, at 25 ppt salinity

chen_chen_30C_25ppt<-data.frame(temp= c(32, 33, 34, 35, 36),
                        alive=c(14, 6, 1, 0, 0),
                        dead=c(6, 14, 19, 20, 20))

mod.chen_chen_30C_25ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_30C_25ppt)
dose.p(mod.chen_chen_30C_25ppt, p=0.5)

################## 30 ppt salinity #####################

# Data for animals acclimated to 20C, at 30 ppt salinity

chen_chen_20C_30ppt<-data.frame(temp= c(30, 31, 32, 33, 34),
                        alive=c(18, 12, 9, 1, 0),
                        dead=c(2, 8, 11, 19, 20))

mod.chen_chen_20C_30ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_20C_30ppt)
dose.p(mod.chen_chen_20C_30ppt, p=0.5)


# Data for animals acclimated to 25C, at 30 ppt salinity

chen_chen_25C_30ppt<-data.frame(temp= c(31, 32, 33, 34, 35),
                        alive=c(18, 10, 2, 0, 0),
                        dead=c(2, 10, 18, 20, 20))

mod.chen_chen_25C_30ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_25C_30ppt)
dose.p(mod.chen_chen_25C_30ppt, p=0.5)


# Data for animals acclimated to 30C, at 30 ppt salinity

chen_chen_30C_30ppt<-data.frame(temp= c(32, 33, 34, 35, 36),
                        alive=c(12, 4, 1, 0, 0),
                        dead=c(8, 16, 19, 20, 20))

mod.chen_chen_30C_30ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_30C_30ppt)
dose.p(mod.chen_chen_30C_30ppt, p=0.5)



################## 35 ppt salinity #####################

# Data for animals acclimated to 20C, at 35 ppt salinity

chen_chen_20C_35ppt<-data.frame(temp= c(30, 31, 32, 33, 34),
                        alive=c(18, 4, 1, 0, 0),
                        dead=c(2, 16, 19, 20, 20))

mod.chen_chen_20C_35ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_20C_35ppt)
dose.p(mod.chen_chen_20C_35ppt, p=0.5)


# Data for animals acclimated to 25C, at 35 ppt salinity

chen_chen_25C_35ppt<-data.frame(temp= c(31, 32, 33, 34, 35),
                        alive=c(17, 8, 1, 0, 0),
                        dead=c(3, 12, 19, 20, 20))

mod.chen_chen_25C_35ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_25C_35ppt)
dose.p(mod.chen_chen_25C_35ppt, p=0.5)


# Data for animals acclimated to 30C, at 35 ppt salinity

chen_chen_30C_35ppt<-data.frame(temp= c(32, 33, 34, 35, 36),
                        alive=c(11, 3, 1, 0, 0),
                        dead=c(9, 17, 19, 20, 20))

mod.chen_chen_30C_35ppt<-glm(cbind(alive, dead) ~ temp, family=binomial, data=chen_chen_30C_35ppt)
dose.p(mod.chen_chen_30C_35ppt, p=0.5)

```

# Lohr et al. 1996

We can convert survival at different temperatures to the temperature animals can tolerate for 1 hour according to Jorgensen et al. 2018, 2021 and Rezende et al. 2014. 


```{r}
static = data.frame(group=c("8.4C_acc", "8.4C_acc", "8.4C_acc", "8.4C_acc", "16C_acc", "16C_acc", "16C_acc", "16C_acc", "20C_acc", "20C_acc", "20C_acc"), 
                    t_coma=c(547, 17, 5.5, 2, 2593, 111.5, 15, 2, 254.5, 27.5, 3), 
                    assay_temp=c(24, 26, 28, 30, 24, 26, 28, 30, 26, 28, 30))

mod.8.4C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="8.4C_acc"))
chemCal::inverse.predict(mod.8.4C, log10(60))
chemCal::inverse.predict(mod.8.4C, 0)

mod.16C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="16C_acc"))
chemCal::inverse.predict(mod.16C, log10(60))
chemCal::inverse.predict(mod.16C, 0)

mod.20C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="20C_acc"))
chemCal::inverse.predict(mod.20C, log10(60))
chemCal::inverse.predict(mod.20C, 0)

```


# Bishai 1960

We can convert survival at different temperatures to the temperature animals can tolerate for 1 hour according to Jorgensen et al. 2018, 2021 and Rezende et al. 2014. 


```{r}
### Data for Salmo salar

static.salar = data.frame(group=c("5C_acc", "5C_acc", "5C_acc", "5C_acc", "10C_acc", "10C_acc", "10C_acc", "20C_acc", "20C_acc", "20C_acc"), 
                    t_coma=c(60, 120, 180, 360, 60, 120, 720, 600, 720, 2880), 
                    assay_temp=c(25, 24, 23, 22.5, 26, 25, 24, 26, 25, 24))

mod.5C.salar<-lm(log10(t_coma)~assay_temp, data=subset(static.salar, group=="5C_acc"))
chemCal::inverse.predict(mod.5C.salar, log10(60))
chemCal::inverse.predict(mod.5C.salar, 0)

mod.10C.salar<-lm(log10(t_coma)~assay_temp, data=subset(static.salar, group=="10C_acc"))
chemCal::inverse.predict(mod.10C.salar, log10(60))
chemCal::inverse.predict(mod.10C.salar, 0)

mod.20C.salar<-lm(log10(t_coma)~assay_temp, data=subset(static.salar, group=="20C_acc"))
chemCal::inverse.predict(mod.20C.salar, log10(60))
chemCal::inverse.predict(mod.20C.salar, 0)

## Data for the sea trout

static.sea = data.frame(group=c("5C_acc", "5C_acc", "5C_acc", "5C_acc", "10C_acc", "10C_acc", "10C_acc", "20C_acc", "20C_acc", "20C_acc"), 
                    t_coma=c(60, 1020, 1440, 1440, 60, 180, 2880, 420, 840, 3600), 
                    assay_temp=c(25, 24, 23, 22.5, 26, 25, 24, 26, 25, 24))

mod.5C.sea<-lm(log10(t_coma)~assay_temp, data=subset(static.sea, group=="5C_acc"))
chemCal::inverse.predict(mod.5C.sea, log10(60))
chemCal::inverse.predict(mod.5C.sea, 0)

mod.10C.sea<-lm(log10(t_coma)~assay_temp, data=subset(static.sea, group=="10C_acc"))
chemCal::inverse.predict(mod.10C.sea, log10(60))
chemCal::inverse.predict(mod.10C.sea, 0)

mod.20C.sea<-lm(log10(t_coma)~assay_temp, data=subset(static.sea, group=="20C_acc"))
chemCal::inverse.predict(mod.20C.sea, log10(60))
chemCal::inverse.predict(mod.20C.sea, 0)


## Data for the sea trout

static.brown = data.frame(group=c("5C_acc", "5C_acc", "5C_acc", "5C_acc", "10C_acc", "10C_acc", "10C_acc", "20C_acc", "20C_acc", "20C_acc"), 
                    t_coma=c(60, 3720, 6000, 7800, 720, 1440, 4320, 1440, 2160, 5160), 
                    assay_temp=c(25, 24, 23, 22.5, 26, 25, 24, 26, 25, 24))

mod.5C.brown<-lm(log10(t_coma)~assay_temp, data=subset(static.brown, group=="5C_acc"))
chemCal::inverse.predict(mod.5C.brown, log10(60))
chemCal::inverse.predict(mod.5C.brown, 0)

mod.10C.brown<-lm(log10(t_coma)~assay_temp, data=subset(static.brown, group=="10C_acc"))
chemCal::inverse.predict(mod.10C.brown, log10(60))
chemCal::inverse.predict(mod.10C.brown, 0)

mod.20C.brown<-lm(log10(t_coma)~assay_temp, data=subset(static.brown, group=="20C_acc"))
chemCal::inverse.predict(mod.20C.brown, log10(60))
chemCal::inverse.predict(mod.20C.brown, 0)

```



# Ebel 1971   

We can convert survival at different temperatures to the temperature animals can tolerate for 1 hour according to Jorgensen et al. 2018, 2021 and Rezende et al. 2014. 


```{r}
### Data for coho salmon

static.coho = data.frame(group=c("5C_acc_NS", "5C_acc_NS", "5C_acc_NS", "5C_acc_NS", "5C_acc_NS", "5C_acc_NS",
                                  "5C_acc_SS", "5C_acc_SS", "5C_acc_SS", "5C_acc_SS", "5C_acc_SS", "5C_acc_SS",
                                  "10C_acc_NS", "10C_acc_NS", "10C_acc_NS", "10C_acc_NS", "10C_acc_NS",
                                  "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", 
                                  "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS",
                                  "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", 
                                  "20C_acc_NS", "20C_acc_NS", "20C_acc_NS", "20C_acc_NS", "20C_acc_NS", "20C_acc_NS",
                                  "20C_acc_SS", "20C_acc_SS", "20C_acc_SS", "20C_acc_SS", "20C_acc_SS", "20C_acc_SS"), 
                    t_coma=c(810, 605, 577, 390, 266, 21.5,
                             626, 580, 435, 229, 186, 20, 
                             1085, 540, 550, 192, 23, 
                             960, 480, 480, 282.5, 193.5, 35.5,
                             555, 502.5, 517.5, 645, 79, 20.5,
                             247, 115, 124.5, 86, 52.5, 38,  
                             810, 780, 840, 197, 43, 20,
                             317.5, 570, 266, 115, 42.5, 16), 
                    assay_temp=c(5, 10, 15, 20, 23, 25,
                             5, 10, 15, 20, 23, 25, 
                             15, 20, 23, 25, 27, 
                             10, 15, 20, 23, 25, 27,
                             15, 20, 23, 26, 27, 28,
                             15, 20, 23, 26, 27, 28, 
                             20, 23, 25, 27, 28, 29,
                             20, 23, 25, 27, 28, 29))
# NS groups

mod.5C.coho.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="5C_acc_NS"))
chemCal::inverse.predict(mod.5C.coho.NS, log10(60))
chemCal::inverse.predict(mod.5C.coho.NS, 0)

mod.10C.coho.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="10C_acc_NS"))
chemCal::inverse.predict(mod.10C.coho.NS, log10(60))
chemCal::inverse.predict(mod.10C.coho.NS, 0)

mod.15C.coho.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="15C_acc_NS"))
chemCal::inverse.predict(mod.15C.coho.NS, log10(60))
chemCal::inverse.predict(mod.15C.coho.NS, 0)

mod.20C.coho.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="20C_acc_NS"))
chemCal::inverse.predict(mod.20C.coho.NS, log10(60))
chemCal::inverse.predict(mod.20C.coho.NS, 0)

# SS groups

mod.5C.coho.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="5C_acc_SS"))
chemCal::inverse.predict(mod.5C.coho.SS, log10(60))
chemCal::inverse.predict(mod.5C.coho.SS, 0)

mod.10C.coho.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="10C_acc_SS"))
chemCal::inverse.predict(mod.10C.coho.SS, log10(60))
chemCal::inverse.predict(mod.10C.coho.SS, 0)

mod.15C.coho.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="15C_acc_SS"))
chemCal::inverse.predict(mod.15C.coho.SS, log10(60))
chemCal::inverse.predict(mod.15C.coho.SS, 0)

mod.20C.coho.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.coho, group=="20C_acc_SS"))
chemCal::inverse.predict(mod.20C.coho.SS, log10(60))
chemCal::inverse.predict(mod.20C.coho.SS, 0)


## Data for chinook salmon

static.chinook = data.frame(group=c(
                                  "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS",
                                  "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", 
                                  "20C_acc_NS", "20C_acc_NS", "20C_acc_NS", "20C_acc_NS", "20C_acc_NS", "20C_acc_NS",
                                  "20C_acc_SS", "20C_acc_SS", "20C_acc_SS", "20C_acc_SS", "20C_acc_SS", "20C_acc_SS"), 
                    t_coma=c(
                             675, 820, 540, 255, 52.5, 10.5,
                             315, 165, 123, 122.5, 16.5, 6, 
                             450, 435, 570, 97, 48.5, 17, 
                             75, 176, 42.5, 44, 22, 6.5), 
                    assay_temp=c(
                             15, 20, 23, 26, 27, 28,
                             15, 20, 23, 26, 27, 28, 
                             20, 23, 25, 27, 28, 29,
                             20, 23, 25, 27, 28, 29))
# NS groups

mod.15C.chinook.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.chinook, group=="15C_acc_NS"))
chemCal::inverse.predict(mod.15C.chinook.NS, log10(60))
chemCal::inverse.predict(mod.15C.chinook.NS, 0)

mod.20C.chinook.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.chinook, group=="20C_acc_NS"))
chemCal::inverse.predict(mod.20C.chinook.NS, log10(60))
chemCal::inverse.predict(mod.20C.chinook.NS, 0)

# SS groups

mod.15C.chinook.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.chinook, group=="15C_acc_SS"))
chemCal::inverse.predict(mod.15C.chinook.SS, log10(60))
chemCal::inverse.predict(mod.15C.chinook.SS, 0)

mod.20C.chinook.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.chinook, group=="20C_acc_SS"))
chemCal::inverse.predict(mod.20C.chinook.SS, log10(60))
chemCal::inverse.predict(mod.20C.chinook.SS, 0)



## Data for steelhead

static.steel = data.frame(group=c(
                                  "10C_acc_NS", "10C_acc_NS", "10C_acc_NS", "10C_acc_NS", "10C_acc_NS", "10C_acc_NS",
                                  "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", "10C_acc_SS", 
                                  "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS", "15C_acc_NS",
                                  "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS", "15C_acc_SS"), 
                    t_coma=c(
                             307, 340, 493, 450, 165, 17,
                             104, 75, 105, 74, 38, 15,
                             840, 630, 645, 435, 58, 23.5,
                             45, 94, 52.5, 43, 19, 19), 
                    assay_temp=c(
                             10, 15, 20, 23, 25, 27,
                             10, 15, 20, 23, 25, 27,
                             15, 20, 23, 26, 27, 28,
                             15, 20, 23, 26, 27, 28 ))
# NS groups

mod.10C.steel.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.steel, group=="10C_acc_NS"))
chemCal::inverse.predict(mod.10C.steel.NS, log10(60))
chemCal::inverse.predict(mod.10C.steel.NS, 0)

mod.15C.steel.NS<-lm(log10(t_coma)~assay_temp, data=subset(static.steel, group=="15C_acc_NS"))
chemCal::inverse.predict(mod.15C.steel.NS, log10(60))
chemCal::inverse.predict(mod.15C.steel.NS, 0)


# SS groups

mod.10C.steel.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.steel, group=="10C_acc_SS"))
chemCal::inverse.predict(mod.10C.steel.SS, log10(60))
chemCal::inverse.predict(mod.10C.steel.SS, 0)

mod.15C.steel.SS<-lm(log10(t_coma)~assay_temp, data=subset(static.steel, group=="15C_acc_SS"))
chemCal::inverse.predict(mod.15C.steel.SS, log10(60))
chemCal::inverse.predict(mod.15C.steel.SS, 0)


```

# McCauley 1963 

We can convert survival at different temperatures to the temperature animals can tolerate for 1 hour according to Jorgensen et al. 2018, 2021 and Rezende et al. 2014. 

The data from this study was digitised from figure 2 and imported into a csv file. 

```{r}
static=read_csv("datasets/McCauley_1963.csv")

# Animals acclimated to 15C
mod.15C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="15_acc"))
chemCal::inverse.predict(mod.15C, log10(60))
chemCal::inverse.predict(mod.15C, 0)

# Animals acclimated to 20C
mod.20C<-lm(log10(t_coma)~assay_temp, data=subset(static, group=="20_acc"))
chemCal::inverse.predict(mod.20C, log10(60))
chemCal::inverse.predict(mod.20C, 0)
```




